Aggregation of empirical Wiener estimates

### 2016-07-20 doc/201511_notes/notes.tex

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.9\textwidth]{weight_pdf-snr}
	\caption{PDF of the Wiener coefficients, varying $\hat{\text{snr}}$, for $N = 40$. The mean of each PDF
	is shown as a square on the graph. The Gaussian approximations are shown as
	the dashed curves. The dashed vertical lines indicate $\varphi(\mathbb E\{v_j\})$.}
	\label{fig:wiener_pdf_N}
\end{figure}

@@

The main aim of this analysis was to find an explanation for the good performance of 
the negative weights in the NL-Bayes algorithm. We didn't achieve that objective. 
\emph{The model adopted here is too simple, and it does not replicate the behaviour of the 
NL-Bayes. On the contrary, in this setting thresholding the weights is better.}

However we did learn interesting things which might be usefull in analyzing more
complex models which might be closer to NL-Bayes. \emph{The Wiener filter is biased
(because it damps components with low SNR), and aggregation does not fix the
bias.} Furthermore, \emph{the thresholded coefficients help in reducing the bias} since
they increase the expected value of the coefficient, thus reducing the damping.

In this example we consider a single Gaussian model. Thefore there exists a
unique theoretical Wiener filter.
The situation in non-local Bayes is much more complex. 
A single patch might be part
of different Gaussian models, and for each there is a Wiener filter that needs
to be estimated. 
Furthermore, a pixel receives contributions from different patches that overlap the
pixel. This seems harder to model. In order to model this, one could consider 
the aggregation as an aggregation of images instead of patches. Each image results
from an empirical Wiener filter in a basis. This basis is built with the DCT or
PCA vectors of each non-overlapping patch. For an $s\times s$ patch, there are $s^2$
of these bases, built by shifting the non-overlapping patches. An image is computed
for each basis with a Wiener filter, and these $s^2$ images are aggregated.

>>>>

Figures \ref{fig:wiener_pdf_N} and \ref{fig:wiener_pdf_snr} show some examples of 
the weights distribution, together with the Gaussian approximation, for some values of
$N$ and $\hat{\text{snr}}$.

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.9\textwidth]{weight_pdf-snr}
	\caption{PDF of the Wiener coefficients, varying $\hat{\text{snr}}$, for $N = 40$. The mean of each PDF
	is shown as a square on the graph. The Gaussian approximations are shown as
	the dashed curves. The dashed vertical lines indicate $\varphi(\mathbb E\{v_j\})$.}
	\label{fig:wiener_pdf_snr}
\end{figure}

@@

The model adopted here is too simple, and it does not replicate the behaviour of the 
NL-Bayes. On the contrary, in this setting thresholding the weights is better.

The Wiener filter is biased (because it damps components with low SNR), and
aggregation does not fix the bias. 
Furthermore, the thresholded
coefficients help in reducing the bias since they increase the expected value
of the coefficient, thus reducing the damping.

In this example we consider a single Gaussian model, and consequently a unique
Wiener filter.
The situation in non-local Bayes is more complex. 
A single patch might participate 
in different Gaussian models, each with its own Wiener filter. 
Furthermore, a pixel receives contributions from different patches overlapping
it. This seems harder to model. One could consider the
an aggregation of image estimates instead of patches. Each image results
from an empirical Wiener filter in a basis built with the DCT or
PCA vectors of each non-overlapping patch. For an $s\times s$ patch, there are $s^2$
of these bases, that correspond to shifts of the non-overlapping grid of patches. An
Wiener estimate of the image is computed for each basis, and these $s^2$ images
are aggregated.

This is a different type of aggregation: 
a single observation is filtered in multiple bases, instead filtering multiple
observations in the same basis.
